Temporal ordering and registration of images in studies of developmental dynamics

### 2015-01-25 image_analysis_paper_development2/manuscript.tex
updated tex

@@

>>>>

\graphicspath{{paper_figures/}}

@@

\begin{figure*}[t]
\raisebox{0.75cm}{\textsf{A}}
\hfill
\includegraphics[width=17.5cm]{drosophila_live_imaging_scrambled}

\raisebox{0.75cm}{\textsf{B}}
\hfill
\includegraphics[width=17.5cm]{drosophila_live_imaging_ordered}

\raisebox{4.25cm}{\textsf{C}}
\includegraphics[width=5cm]{drosophila_live_imaging_angle_corr}
%
\hfill
%
\raisebox{4.25cm}{\textsf{D}}
\includegraphics[width=5cm]{drosophila_live_imaging_rank_corr}
%
\hfill
%
\raisebox{4.25cm}{\textsf{E}}
%
\raisebox{2.75cm}{
{ \textsf{ 
\begin{tabular}{ |p{1cm} | p{1.25cm}|  p{1.5cm}| }
\hline
Movie Index & Average Angle Error & Rank Correlation Coefficient \\
\hline
1 & 8.37$^{\circ}$ & 0.9989 \\ 
2 & 4.98$^{\circ}$ & 0.9994 \\ 
3 & 6.47$^{\circ}$ & 0.9795 \\ 
4 & 7.03$^{\circ}$ & 0.9953 \\ 
5 & 3.04$^{\circ}$ & 0.9959 \\ 
 \hline
\end{tabular}}}}

\end{figure*}

\begin{figure*}[t]
\begin{minipage}[b]{14cm}
\raisebox{0.75cm}{\textsf{A}}
\includegraphics[width=13.75cm]{zebrafish_scrambled}

\raisebox{0.75cm}{\textsf{B}}
\includegraphics[width=13.75cm]{zebrafish_ordered}
\end{minipage}
%
\hfill
%
\raisebox{2.5cm}{\textsf{C}}
\includegraphics[width=3.25cm]{zebrafish_rank_corr}

\end{figure*}
